Supplementary information

### 2019-12-11 manuscript/figures.Rmd
changed figure order
swapped index scatter plot and site differences plot from supplementary to figures

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised Random Forest. a) Multidimensional scaling (MDS) plot of random forest proximity values of individual trees scaled to two dimensions. Mean margin value shown. b) Relative descriptor Gini importances measures.',fig.height=5}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```

>>>>

```{r decline_index_plot}
loadd(decline_indexes_plot)

decline_indexes_plot
```

### 2019-12-11 manuscript/supplementary.Rmd
added DAI lime analysis plot to supplementary
swapped index scatter plot and site differences plot from supplementary to figures

@@

```{r decline_index_plot}
loadd(decline_indexes_plot)

decline_indexes_plot
```

@@

>>>>

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised Random Forest. a) Multidimensional scaling (MDS) plot of random forest proximity values of individual trees scaled to two dimensions. Mean margin value shown. b) Relative descriptor Gini importances measures.',fig.height=5}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```

@@

@@

```{r DAIlimeAnalysisPlot,fig.height=8}
loadd(DAI_lime_analysis_plot)

DAI_lime_analysis_plot
```
